\texttt{escheR}: Unified multi-dimensional visualizations with Gestalt principles

### 2023-05-09 Manuscript/manuscript.tex
Adjust acknowledgement order

\subsection*{Acknowledgements}
BG would like to acknowledge Kristen R. Maynard, Nicholas J. Eagles, Mina Ryten, Leon Di Stefano, and Lukas M. Weber for their helpful comments, feedback and suggestions on \texttt{escheR} functionality. Kristen R. Maynard and Nicholas J. Eagles are employed by the Lieber Institute for Brain Development (LIBD); Mina Ryten is employed by University College London; Leon Di Stefano and Lukas M. Weber are from the Johns Hopkins Bloomberg School of Public Health, Department of Biostatistics.

>>>>

\subsection*{Acknowledgements}
BG would like to acknowledge Nicholas J. Eagles, Kristen R. Maynard, Mina Ryten, Leon Di Stefano, and Lukas M. Weber (appearing in alphabetic order of last name) for their helpful comments, feedback and suggestions on \texttt{escheR} functionality. Nicholas J. Eagles and Kristen R. Maynard are employed by the Lieber Institute for Brain Development; Mina Ryten is employed by University College London; Leon Di Stefano and Lukas M. Weber are from the Johns Hopkins Bloomberg School of Public Health, Department of Biostatistics.
